### 2023-05-09 main.tex
ss

We observe that $\forall i,j=1,2,\ldots,N$
\begin{equation}
	\sum_{a,b=1}^{L}e_{ij}^{[a]}e_{ji}^{[b]}=e_{ij}^{tot}e_{ji}^{tot}-e_{ii}^{tot}
\end{equation}
then 
\begin{equation}
	\boxed{A^{2L-1}=e_{11}^{tot}\left(2e_{11}^{tot}+I^{tot}\right)-\sum_{j=2}^{N}e_{jj}^{tot}}=2e_{11}^{tot}\left(e_{11}^{tot}+I^{tot}\right)-L
\end{equation}
{\color{blue}ok?}

@@

\begin{align}
	Q_{2L+2}&=A^{2L+1}-\sum_{i=2}^{N}D_{ii}^{2L+1}{\color{red}=N}\\
	Q_{2L+1}&=NA^{2L+1}+A^{2L}-\sum_{i=2}^{N}D_{ii}^{2L}={\color{red}2+2N}\\
	Q_{2L\phantom{+}}&=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}+\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{align}
The charges $Q_{2L+2}$ and $Q_{2L+1}$ are proportional to the identity matrix, while $Q_{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=2,\ldots,N$.\\
It is easy to show that 
\begin{equation}
	\left[Q_{2L},\widetilde{H}\right]=Q_{2L}\widetilde{H}-\widetilde{H}Q_{2L}=0
\end{equation}
The commutation with the Hamiltonian $\widetilde{H}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. \\
We introduce the following:
\begin{equation}
Q_{2L}^{0}:=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}
\end{equation}
that is 
\begin{equation}
\begin{split}
Q_{2L}^{0}&=NI^{tot}+2e_{11}^{tot}(e_{11}^{tot}+I^{tot})-(N+2)\sum_{j=2}^{N}e_{jj}^{tot}+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
&=N+2e_{11}^{tot}(e_{11}^{tot}+1)-(N+2)(L-e_{11}^{tot})+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
\end{split}
\end{equation}
where we used $
 \sum_{i=1}^N m_i=L$.

>>>>

We observe that $\forall i,j=1,2,\ldots,N$
\begin{equation}
	\sum_{a,b=1}^{L}e_{ij}^{[a]}e_{ji}^{[b]}=e_{ij}^{tot}e_{ji}^{tot}-e_{ii}^{tot}
\end{equation}
then 
\begin{equation}
	\boxed{A^{2L-1}=e_{11}^{tot}\left(2e_{11}^{tot}+I^{tot}\right)-\sum_{j=2}^{N}e_{jj}^{tot}}=2e_{11}^{tot}\left(e_{11}^{tot}+I^{tot}\right)-L
\end{equation}
{\color{blue}ok?}where we used $
 \sum_{i=1}^Ne_{ii}^{tot}=L$.

@@

\begin{align}
	Q_{2L+2}&=A^{2L+1}-\sum_{i=2}^{N}D_{ii}^{2L+1}{\color{red}=N}\\
	Q_{2L+1}&=NA^{2L+1}+A^{2L}-\sum_{i=2}^{N}D_{ii}^{2L}={\color{red}2+2N}\\
	Q_{2L\phantom{+}}&=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}+\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{align}
The charges $Q_{2L+2}$ and $Q_{2L+1}$ are proportional to the identity matrix, while $Q_{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=2,\ldots,N$.\\
It is easy to show that 
\begin{equation}
	\left[Q_{2L},\widetilde{H}\right]=Q_{2L}\widetilde{H}-\widetilde{H}Q_{2L}=0
\end{equation}
The commutation with the Hamiltonian $\widetilde{H}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. \\
We introduce the following:
\begin{equation}
Q_{2L}^{0}:=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}
\end{equation}
that is 
\begin{equation}
\begin{split}
Q_{2L}^{0}&=NI^{tot}+2e_{11}^{tot}(e_{11}^{tot}+I^{tot})-(N+2)\sum_{j=2}^{N}e_{jj}^{tot}+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
&=N+2e_{11}^{tot}(e_{11}^{tot}+1)+(N+2)(e_{11}^{tot}-L)+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
\end{split}
\end{equation}
